On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-09-29 paper/paper.tex
More information about the standard interpretation

>>>>

Recall that the internal representations of \verb|SumMatch a b| and \verb|ProdMatch a b|
are functions of type \verb|a -> b|. These types are unwrapped by the functions

\begin{lstlisting}
runSumMatch :: SumMatch a b -> (a -> b)
runProdMatch :: ProdMatch a b -> (a -> b)
\end{lstlisting}

Given this, the \verb|ProdMatchExp| case of the \verb|prodMatchAbs| function can be
implemented as follows:

\begin{lstlisting}
prodMatchAbs env (ProdMatchExp f) =
  \ pair ->
    case pair of
      (x, y) ->
        runProdMatch (absEnv env f x) y
\end{lstlisting}
